About

### 2025-01-17 about.qmd
Made an email service for the About page

About this site

Contact the site administrators for additional information about protocols, experimental design, and website feedback:

(I am working on making a comment submission form which will send an email to a site admin -- something like ContactUs\@LipidInteractome.org)

>>>>

This repository is still under construction (as you can probably tell). Someday soon this page will have details about the founders of this resource, as well as a data submission form. Until then, please contact the site administrators for additional information about protocols, experimental design, and website feedback:

 <contact.us@LipidInteractome.org>{target="_blank"}
